Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-05-18 supplement/06_bat_data.Rmd
some edits to bats

```{r summarise_counts}
data_heatmap = copy(data)
data_heatmap[, c("xround", "yround") := list(
  plyr::round_any(X, 200),
  plyr::round_any(Y, 200)
)]
data_heatmap = data_heatmap[, .N, by = c("xround", "yround")]
```

```{r plot_heatmap}
fig_heatmap = 
ggplot(data_heatmap)+
  geom_tile(
    aes(
      xround, yround, fill = N
    ),
    colour = "grey",
    size = 0.1,
    show.legend = F
  )+
  scale_fill_viridis_c(
    option = "C",
    direction = -1,
    trans = "log10"
  )+
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)

@@

# make figure
fig_lags = 
ggplot(data_for_intervals)+
  geom_histogram(
    aes(
      x = lag / 8
    ),
    bins = 15,
    fill = "grey",
    col = "black"
  )+
  geom_vline(
    xintercept = 1,
    col = "red"
  )+
  scale_x_log10(
    labels = function(x) {sprintf("%ix", x)}
  )+
  scale_y_sqrt()+
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  )+
  labs(x = "Sampling interval")

@@

```{r localisation_error}
fig_error_histogram = 
ggplot(data)+
  geom_histogram(
    aes(
      x = sqrt(VARX)
    ),
    bins = 15,
    fill = "grey",
    col = "black"
  )+
  scale_x_log10(
    labels = function(x) {sprintf("%2.fm", x)}
  )+
  scale_y_sqrt()+
  coord_cartesian(
    xlim = c(0.5, 5e3)
  )+
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  )+
  labs(x = "Variance X")

@@

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_speed <-
  ggplot() +
  geom_point(
    data = data[!data_split,
      on = c("TAG", "X", "Y", "TIME")
    ],
    aes(X, Y),
    col = "grey",
    shape = 4
  ) +
  geom_path(
    data = data_split,
    aes(X, Y,
      col = TAG
    ),
    size = 0.3,
    show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(
    crs = 2039,
    xlim = range(data_split$X),
    ylim = range(data_split$Y)
  )
```

>>>>

```{r summarise_counts}
data_heatmap = copy(data)
data_heatmap[, c("xround", "yround") := list(
  plyr::round_any(X, 250),
  plyr::round_any(Y, 250)
)]
data_heatmap = data_heatmap[, .N, by = c("xround", "yround")]
```

```{r plot_heatmap}
fig_heatmap = 
ggplot(data_heatmap)+
  geom_tile(
    aes(
      xround, yround, fill = N
    ),
    colour = "grey",
    size = 0.1,
    show.legend = F
  )+
  scale_fill_viridis_c(
    option = "C",
    direction = 1,
    trans = "log10"
  )+
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)

@@

# make figure
fig_lags = 
ggplot(data_for_intervals)+
  geom_histogram(
    aes(
      x = lag / 8,
      fill = (lag / 8 > 3)
    ),
    position = position_identity(),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  )+
  geom_vline(
    xintercept = 1,
    col = "red"
  )+
  scale_x_log10(
    labels = function(x) {sprintf("%ix", x)},
    breaks = c(1, 3, 10, 100, 1000)
  )+
  scale_y_sqrt()+
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  )+
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  )+
  labs(x = "Sampling interval")

@@

```{r localisation_error}
fig_error_histogram = 
ggplot(data)+
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  )+
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  )+
  scale_x_log10(
    labels = function(x) {sprintf("%2.fm", x)}
  )+
  scale_y_sqrt()+
  coord_cartesian(
    xlim = c(0.5, 5e3)
  )+
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  )+
  labs(x = "Variance X")

@@

```{r echo=FALSE}
# now plot over raw data
fig_bat_filter_speed <-
  ggplot() +
  geom_path(
    data = data,
    aes(X, Y, group = TAG),
    col = "black",
    size = 0.3
  ) +
  geom_path(
    data = data_split,
    aes(X, Y,
      col = TAG
    ),
    # col = "grey20",
    # size = 0.3,
    show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(
    crs = 2039,
    xlim = range(data_split$X),
    ylim = range(data_split$Y)
  )
```
